Accuracy and precision of zero-heat-flux temperature monitoring

### 2019-12-06 manuscript/manuscript.Rmd
fixed reference for r core team

Measures of uncertainty were included in our meta-analyses by calculating the outer 95% confidence intervals for pooled limits of agreement. We also accounted for repeated measurements if they were not properly adjusted for in individual studies. This was achieved by using weights proportional to the number of participants, not the total number of measurements.  The R statistical program was used to conduct all analyses.[@team2017r] All data and R code used in the meta-analyses can be located at this [link](https://github.com/awconway/zhf-review).

>>>>

Measures of uncertainty were included in our meta-analyses by calculating the outer 95% confidence intervals for pooled limits of agreement. We also accounted for repeated measurements if they were not properly adjusted for in individual studies. This was achieved by using weights proportional to the number of participants, not the total number of measurements.  The R statistical program was used to conduct all analyses.[@R2018] All data and R code used in the meta-analyses can be located at this [link](https://github.com/awconway/zhf-review).
